---
title: Data Analysis and Visualization
subtitle: Chapter 3. Exploratory Data Analysis in R
author: Iñaki Úcar
institute:
  - Department of Statistics | uc3m-Santander Big Data Institute
  - Bachelor in Data and Business Analytics
date: >
  Licensed under Creative Commons Attribution
  [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/)
  Last generated: `r Sys.Date()`
output:
  xaringan::moon_reader:
    chakra: assets/remark-latest.min.js
    lib_dir: assets
    css: [default, metropolis, metropolis-fonts, assets/theme.css, assets/colors.css]
    nature:
      beforeInit: assets/macros.js
      highlightStyle: vs
      highlightLines: true
      countIncrementalSlides: false
---
class: base24, middle, clear

```{r setup, include=FALSE}
options(htmltools.dir.version=FALSE)
knitr::opts_chunk$set(message=FALSE, warning=FALSE, fig.align="center", dpi=150)
knitr::opts_chunk$set(cache=TRUE, cache.path="ch3_cache/html/")
knitr::opts_chunk$set(fig.path="ch3_files/figure-html/")

library(ggplot2)
theme_set(theme_gray(base_size=16))
```

```{r xaringanExtra, echo=FALSE, cache=FALSE}
xaringanExtra::use_share_again()
xaringanExtra::style_share_again(share_buttons="none")
xaringanExtra::use_scribble()
xaringanExtra::use_panelset(in_xaringan=TRUE)
```

- [Types of Data](ch3.html#3)
- [Catalog of Graphs and Applications](ch3_1.html#2)

---
class: inverse, center, middle

# Types of Data

---
class: base24

# Forms of Data

--

### Entities

- The objects of interest, what we wish to visualize (e.g. a *sale*)
- Also known as **observations**, **records**, **instances**, **cases**...

--

### Relations

- Relationships between entities (e.g. a *customer* makes a *sale*)
- Many kinds: hierarchical, network, temporal, causal...
- Sometimes provided explicitly (e.g. edges in a network),
  sometimes its discovery is the purpose of the visualization (e.g. correlation)

--

### Attributes

- Properties of entities and relations (e.g. *price* and the *profit* of a sale)
- Also known as **features**, **variables**, **covariates**, **dimensions**...
- Can be qualitative or quantitative

---

# Types of Attributes

--

### Stevens' typology of measurement scales (1946)

- **Nominal**: purely qualitative, categories without order (e.g. fruits)
- **Ordinal**: qualitative with order (e.g. weekdays)
- **Interval**: quantitative data with no zero point (e.g. time of departure)
- **Ratio**: quantitative data with zero point (e.g. money)

--

### In practice

.font120[
- **Categorical data**: nominal or ordinal (e.g. fruits, weekdays)
- **Discrete data**: ordered categories or counts (e.g. number of visits)
- **Continuous data**: interval or ratio (e.g. time, money)
]

--

### Uncertainty

- Continuous data often come with a measure of uncertainty
- Can be represented as an additional attribute (e.g. confidence interval)
- Visualization of uncertainty is important but often overlooked

---
class: base24

# Data Analysis

.pull-left[
## Tidy Data

$N\times P$ data frame:

|      | Attr1 | Attr2 | Attr3 | ... | AttrP |
|-----:|------:|------:|------:|----:|-------|
| Obs1 |       |       |       |     |       |
| Obs2 |       |       |       |     |       |
| Obs3 |       |       |       |     |       |
|  ... |       |       |       |     |       |
| ObsN |       |       |       |     |       |
]

.pull-right[
## Data Dimensions

- One dimension:<br>**univariate** analysis
- Two dimensions:<br>**bivariate** analysis
- More than two dimensions:<br>**multivariate** analysis
]
